Missing data: Current practice in football research and recommendations for

### 2020-10-10 paper/paper.Rmd
format missing data overplot figure.

```{r libraries, message = FALSE}
library(tidyverse)
library(naniar)
library(visdat)
library(patchwork)
library(fitzRoy)
library(mice)
library(truncnorm)
library(janitor)
```

@@

aq_vis_miss <- vis_miss(data_plot)

aq_upset <- gg_miss_upset(data_plot)

aq_fct <- gg_miss_fct(data_plot, team)

gg_miss_scatter <- ggplot(data_plot,
       aes(x = sprint_distance,
           y = sprints)) +
  geom_miss_point()

@@

cowplot::plot_grid(aq_vis_miss,
                   # aq_upset,
                   aq_fct,
                   gg_miss_scatter,
                   aq_miss_var, 
                   align = "hv",
                   labels = "AUTO")

@@

# Supplement 3

>>>>

```{r libraries, message = FALSE}
library(tidyverse)
library(naniar)
library(visdat)
library(patchwork)
library(fitzRoy)
library(mice)
library(truncnorm)
library(janitor)
library(cowplot)
```

@@

aq_vis_miss <- vis_miss(data_plot) #+ 
  #theme(text = element_text(size = 14))

aq_fct <- gg_miss_fct(data_plot, team) + 
  #theme(text = element_text(size = 14)) +
  labs(x = "Team", y = "Variable")

gg_miss_scatter <- ggplot(data_plot,
       aes(x = sprint_distance,
           y = sprints)) +
  geom_miss_point(size = 2) + 
  theme_minimal() +
  #theme(text = element_text(size = 14)) +
  labs(x = "Total sprint distance (m)", y = "Number of sprints (count)", colour = "Missing")

@@

# Grid plots
cowplot::plot_grid(aq_vis_miss, aq_fct, gg_miss_scatter, aq_miss_var, 
                   nrow = 2,
                   ncol = 2,
                   align = "hv",
                   axis = "tblr",
                   label_size = 20,
                   labels = "AUTO")
```

@@
